% Preamble
\documentclass[11pt]{article}

% Packages
\usepackage{amsmath}

% Document
\begin{document}
    We developed a pipeline for the localization of our moving vehicle using images or videos captured by
    a vehicle-mounted camera. Our process involved capturing videos of the streets in Padova, extracting
    video frames, and applying the Structure from Motion algorithm. We used \cite{lindenberger2021pixsfm}
    to refine our reconstruction. Furthermore, some handcrafted methods are applied as preprocessing before
    registration, like aligning on the z axis, filtering, and slicing. Then, the template matching algorithm
    localized the ground 3D points in a small windows of the city aerial point cloud. Our extended template matching
    algorithm returned not only the coordinates but also the scale and rotation of the template ground point cloud.
    Next, we scaled and transformed our main ground point cloud with these results into aerial point cloud, and then,
    we employed the Iterative Closest Point (ICP) algorithm which is a common local registration algorithm for
    point clouds. And the results became much more accurate.

    As it is discussed before, it is extremely hard to register the ground point cloud in the aerial point cloud
    since the only common 3D points between these two are streets and ground points, and these points
    are not so discriminative. However, our method simplified the problem and showed a reasonable performance
    in local point cloud registration.

    As it is observed in the match results, the bigger the window of the aerial point cloud is, the harder it is to localize.
    Therefore, we may think of another approach for global registration. In our experiments, it is noticed that by
    looking at both point clouds from top viewpoint, crossroads are differentiable. So, if we could detect them as
    keypoints and provide a proper descriptor for each crossroad, it is possible to register by correspondences
    the ground point cloud in wider windows of the aerial point cloud. Our deep learning approach showed it is
    possible to filter the crossroads by generating the binary grid maps as input to our model. However, we have to
    prepare a huge dataset of crossroads which needed a longer time for this thesis.

\end{document}